\chapter{Introduction to Modules}
\section{\textbf{Definition of Module}}
\begin{defn}  [\textbf{Left Module}]

 Let $ R $ be a ring with identity and $ M $ be an abelian group with addition. We say $ M $ is a left $R-$module if there exists a mapping\footnote{often called as scaler multiplication.}
\begin{equation*}
R \times M \rightarrow M
\end{equation*}	
defined by
\begin{equation*}
(a \ , \ x) \rightarrow ax
\end{equation*}\marginnote[-2em]{$\forall \ a \in \ R$ and $x$ $\in \ M$}
satisfying following properties :
\begin{align}
(a+b) x =& ax + bx \\ a(x+y) =& ax + ay \\ (ab)x =& a(bx) \\ 1x =& x
\end{align}\marginnote[-7em]{\large{$\forall$ $ a\ , \ b \in R$ \newline $x \ , y \ \in M$}}
and denoted by $_{R}M$
\end{defn}
\bigskip
\begin{defn}[\textbf{Right Module}]
 Let $ R $ be a ring with identity and $ M $ be an abelian group with addition. We say $ M $ is a right $R-$module if there exists a mapping
\begin{equation*}
M \times R \rightarrow M
\end{equation*}	
defined by
\begin{equation*}
(x \ ,\ a) \rightarrow xa
\end{equation*}
\marginnote[-1em]{$ \forall \ a$ $\in$ $R$ and $x$ $\in$ $M$} satisfying following properties\marginnote[4em]{\large{$\forall$ $ a\ , \ b \in R$ \newline $x \ , y \ \in M$}} :
\begin{align}
x (a+b)  &= xa + xb \\ (x+y) a &= xa + ya \\ x (ab) &= (xa)b \\ x1 &= x
\end{align}
and denoted by $M_{R}$.         \end{defn}

\subsection{Examples :}
\begin{enumerate}
\item Let $V$ be a vector space over a field $F$ then $V$ is a left as well as right $F-$Module.\newline \bigskip
\item Let $G$ be any abelian group under addition , then $G$ is a $\mathbb{Z-}$Module where $\mathbb{Z}$ is set of integers.\newline \bigskip
\item Let $R$ be ring and $M= R[x]$ \marginnote{Suppose ring $R$ is a field then $R-$Module $R[x]$ is a vector space over field $R$.} where $R[x]$ is a group of all polynomials with coefficents in $R$ then $M$ is a left as well as a right $R-$Module with scaler multiplication being usual multiplication.\newline \bigskip
\item Let $M$ be collection of all $m \times n $ matrices over ring $R$ , then $M$ is left $R-$Module where scaler multiplication being usual multiplication of a scaler to a matrix. \newline
\bigskip
In particular, if $M$ is a set of $1 \times n$ matrices over $R$ or $M = R^n$(set of $n-$tuples) then $R^n$ is a left $R-$module.
\end{enumerate}
\bigskip
\begin{remark}
	Let $R$ be a commutative ring then every left $R-$module can be transformed to right $R-$module and vice-versa.
	\end{remark}
\begin{proof} Let $M$ be left $R-$module and $R$ be a commutative ring. \newline
	so, $\exists$ a mapping
\begin{equation*}
R \times M \rightarrow M
\end{equation*}	
defined by
\begin{equation*}
(a \ , \ x) \rightarrow ax
\end{equation*}
for each $a$ $\in$ $R$ and $x$ $\in$ $M$ satisfying following properties :
\marginnote{$\forall$ $ a\ , \ b \in R$ and $x \ , y \ \in M$  }
\begin{eqnarray*}
(a+b) x &=& ax + bx \\ a(x+y) &=& ax + ay \\ (ab)x &=& a(bx) \\ 1x &=& x
\end{eqnarray*}
$\because \ R$ is a commutative ring.\newline
Now, Define an another mapping
 \begin{equation*}
 M \times R \rightarrow M
 \end{equation*}	
 defined by
 \begin{equation*}
 (x \ ,\ a) \rightarrow x*a \ = \ ax
 \end{equation*}
To check $M$ is a right $R-$Module , we need to verify properties number \ref{eq1.5}-\eqref{eq1.8}
 \begin{description}
 	\item[(i) Distribuitive Law]
 	\begin{align*}
 		x*(a+b) &= (a+b)x \\ &= ax + bx \\ &= (x*a) + (x*b)
 	\end{align*}
 	\item[(ii) Distributive Law] \begin{align*}
 		(x+y)*a &= a(x+y) \\ &= ax + ay \\ &= (x*a) + (y*a)
 	      \end{align*}
       \item[(iii)]  \begin{align*}
       x*(ab) &= (ab)x \\ &= (ba)x \\ &= b(ax) \\ &= (ax)*b
       \end{align*}
   \item[(iv)] \begin{align*}
   x*1 &= 1x \\  &= x
   \end{align*}
Thus, $_{R}M$ is transformed to $M_R$.\newline
Similarly, Converse statement can be verified.
\end{description}
\end{proof} \bigskip
\begin{remark}
	Let $S$ be a subring of ring $R$ then $_{S}M$ exists \marginnote{by existance means $M$ is a valid left module over mentioned ring or subring. i.e. satisfying those four properties.}  only if $_{R}M$ exists.
\end{remark} \bigskip
\begin{remark}
	Same Abelian group\marginnote{For Instance,  The field $\mathbb{R}$ is $\mathbb{R}-$module,$\mathbb{Q}-$module and $\mathbb{Z}-$module.} can have the structure of a Module for a number of different rings.
\end{remark} \bigskip
\begin{remark}
Let $I$ be left ideal of $R$ then quotient ring $\bigslant{R}{I}$ is a left $R$-module.\marginnote{Here scaler multiplication is \newline \begin{equation*}
	R \times \bigslant{R}{I} \rightarrowtail \bigslant{R}{I}
	\end{equation*}
defined as
\begin{equation*}
(a \ , \ x+I) \rightarrowtail ax+I
\end{equation*}

$\forall \ a \in R$ and $\forall \ x+I \in \bigslant{R}{I}$}

\end{remark}
\begin{proof}[verification:]
	Left to reader\newline \bigskip
	\textbf{Hint:} you need to verify those four properties: \eqref{eq1.1}-\eqref{eq1.4}
\end{proof}
\bigskip

\begin{thm}{\textbf{(Elementry Properties:)}}\newline
	Let $M$ be a left $R$-module . Suppose $0_m \ \text{and} \ 0_r$ denotes additive identities of $M$ and $R$ respectively. Then,  for each $x \ \in M$ and $r \ \in R$ \newline
\begin{description}
\item (i)
	\begin{equation*}
	0_m = 0_r\ x = r\ 0_m
	\end{equation*}
\item (ii)
	\begin{equation*}
	r(-x) =  (-r)x = -rx
	\end{equation*}
\end{description}
\end{thm}
\begin{proof}
	\begin{description}
		\item[(i)]
As $0_m$ is the additive identity of $M$. so, $0_m = 0_m + 0_m$\newline
Consider \marginnote{$ \because \ (r\ ,\ 0_m)\rightarrowtail r\ 0_m \in M$\newline so, $r\ 0_m = r\ 0_m + 0_m$}
 $ r(0_m + 0_m) = r\ 0_m  = r\ 0_m +0_m $\newline
but, $r(0_m + 0_m) = (r\ 0_m) +(r\ 0_m)$ \marginnote{
	$ \because \ M$ is a left $R$-module.\newline (using distribuitive property)}\newline
so, we have \begin{equation*}
r\ 0_m +r\ 0_m = r\ 0_m + 0_m
\end{equation*}
as ($M,+$) is an abelian group so left and right cancellation law holds.
\begin{eqnarray*}
\cancel{r\ 0_m} +r\ 0_m &=& \cancel{r\ 0_m} + 0_m \\ r\ 0_m &=& 0_m
\end{eqnarray*}
a similiar argument can be used to prove $0_m = 0_r\ x$.
\item[(ii)]
as $M$ is a left $R$-module so $(r \ , x )\ \rightarrowtail rx \in M$ \newline
Now, Consider $(-r)x + rx$
\begin{eqnarray*}
\text{using distribuitive law} \\ (-r)x + rx &=& (-r + r)x \\  &=& 0_r \ x \\ &=& 0_m
\end{eqnarray*}
i.e. $(-r)x$ is additive inverse of  $(rx)$ but additive inverse of $(rx)$ is $-rx$ and it is unique for an abelian group($M$ here)
\begin{equation*}
\therefore \ (-r)x = -rx
\end{equation*}
a similar argument can be used to prove that $r(-x)  = -r x$.
\end{description}
\end{proof}
\bigskip
\begin{defn}[ \textbf{Ring Homomorphism}]
	Let\marginnote{often called as ring homo} $R$ and $S$ be two rings with identities $1_r \ , 1_s$ respectively then a map(say $f$)
	\begin{equation*}
	f : R \rightarrow S
	\end{equation*}
	is said to be a ring homomorphism or ring linear map if for every $a \ ,\ b \in R$ following properties holds\marginnote[-2.55em]{if $R$ = $S$ then we call ring homo as ring endomorphism. For instance , let $f$ be ring homo from $R$ to $R$ . we say $f$ is endomorphism of $R$ and denoted by $End \ R$}
	\begin{description}
		\item[(i) \centering{Preserves Addition}]\begin{equation*}
		(a+b)f = (a)f +(b)f
		\end{equation*}
		\item[(ii) \centering{Preservers Multiplication} ]\begin{equation*}
		(ab)f = (a)f . (b)f
		\end{equation*}
		\item[(iii) \centering{ Maps identity to identity}]\begin{equation*}
		(1_r)f = 1_s
		\end{equation*}
	\end{description}
\end{defn}
\begin{remark}
	Such a mapping need not to be bijective. if it is bijective then we say it is a ring isomorphism or rings are isomorphic.
\end{remark}
\bigskip
\begin{thm}
	Let\marginnote{\[ M \ \text{is a right R-module} \] \[\centering\Updownarrow \] \[\newline\exists \ f: R \ \xrightarrow[\text{Homo}]{\text{Ring}} End \ M \] } $R$ be a ring and $M$ be any abelian group with addition. then $M$ is a right $R$-module if and only if there exists a map which is ring homomorphism from $R$ to $End \ M$
\end{thm}
\begin{proof}
\begin{description}
	\item[(Forward Part)\newline]
	Let us suppose that $ M $ is a right $ R $-module.\newline
	\textbf{Claim:} there exists a map which is ring homomorphism from $R$ to $End \ M$\newline
   $ \because \ M  $ is a left $ R $-module , so there exist a map\newline
   \[ f: M \times R \rightarrowtail M  \]
   defined by
   \[ (x \ , a) \rightarrowtail ax \]
   satisfying following properties:
    \begin{align*} (x+y)a &= (x)a+(y)a \\
     x(a+b)\mathnote{ $$\forall \ x , y \ \in M \ \&  \ a ,b \in R$$ } &= xa + xb \\
     x(ab) &= (xa)b \\
     x 1 &= x
     \end{align*}
   for each $ a \in R $ , define a map(say $\phi_a $)
   \[ \phi_a: M\rightarrowtail\ M \]
   such that for each $x\in  M$
   \[ (x )\phi_a = xa \in \ M \]
   Now, we'll show that $ \phi_a \in \ End \ M $\newline
   Let $ x , y \in M $ \newline Consider  $  (x+y)\phi_a$
   \begin{align*}
   	&= (x+y)a  \\ &= xa + ya  \\ &= (x)\phi_a + (y)\phi_a
   \end{align*}\marginnote[-5.5em]{using defination of $\phi_a$} \marginnote[-4em]{using \eqref{eq1.9}}
   so, $\phi_a$ preserves addition and is a group homo from $M$ to $M$.
   \newline i.e. $\phi_a \in End \ M$ \newline
   Now, we can define a map (say $f$)
   \begin{align*}
   &f : R \rightarrowtail End \ M \\ \text{defined as} \\&(a)f \rightarrowtail \phi_a \mathnote{$\forall a \in R$ and $\phi_a \in End \ M$}
   \end{align*}
Now, We'll show that $ f $ is a ring homomorphism.\newline
\begin{description}
	\item[(A)]
	  \begin{align*}
	(a+b)f &= \phi_{a+b}
	\mathnote{\[ \text{for each}\  x \in M \ \text{we have,}\] \begin{align*}
		(x)\phi_{a+b} &= x(a+b) \ =xa+xb \\ &=(x)\phi_a +(y)\phi_b \\ \therefore \ \phi_{a+b} &= \phi_a +\phi_b
		\end{align*}}
		  \\  &= \phi_a +\phi_b \\&= (a)f +(b)f
	\end{align*}
    \item[(B)] \begin{align*}
    (ab)f &= \phi_{ab}\mathnote{\[ \text{for each}\  x \in M \ \text{we have,}\] \begin{align*} (x)\phi_{ab} &= x(ab)   = (xa)b \\ &= (xa)\phi_b = (x)\phi_a \centerdot\phi_b \\ \therefore \ \phi_{ab} &= \phi_a\centerdot\phi_b \end{align*} } \\  &= \phi_a\centerdot\phi_b \\&= (a)f\ (b)f
    \end{align*}
\item[(C)] \begin{align*}
(1)f\mathnote{\[ \text{for each}\  x \in M \ \text{we have,}\] \begin{align*} (x)\phi_{1} &= x(1) \\&=x \end{align*}\[ \therefore \ \phi_{1} \ \text{is identity of}End \ M \]} &= \phi_{1}
\end{align*}

   \end{description}
\bigskip
Thus, Forward Part is proved.\newline\bigskip
\item[(Converse Part)]
\bigskip
Assume that $\exists$ a ring homo.( say $f$)
\[ f: R\xrightarrow[\text{Homo}]{\text{Ring}} End \ M \]
for any $a \in R$,we denote the $(a)f$ by $f_a \in End \ M$\newline
\textbf{Claim:} $M$ is a right $R$-module.\newline
so let's define a map
\[ R\times M \longrightarrow M \] defined by
\[ (a , x ) \rightarrowtail x*a = (x)f_a \]
to prove $M$ is a right $R$-module , we need to verify four properties $\eqref{eq1.5}$- $\eqref{eq1.9}$ of right $R$-module.
\begin{description}
	\item[(i)]
\end{description}
\begin{align*}
(x+y)*a &= (x+y)f_a \\& = (x)f_a +(y)f_a \mathnote{\[ \because\ f_a \ \in End \ M \]}\\& = x*a + y*a
\end{align*}
   \item{(ii)}
   \begin{align*}
   x*(a+b) &= (x)f_{a+b} \\ &= (x)(f_a + f_b) \mathnote{\[ \because\ f_a \ , \ f_b \in End \ M \]} \\&=(x)f_a + (x)f_b
 \\ &= (x*a) + (x*b)   \end{align*}
 \item{(iii)}
 \begin{align*}
 x*(ab) &= (x)f_{ab} \\ & = (x)f_a\centerdot f_b \\&=(x f_a)f_b \\&= (x*a)*b
 \end{align*}
 \item{(iv)}
 \[ x*1 = (x)f_1  = x\]\marginnote{\[ \because\ f_1 \text{is identity in} End \ M \]}
Thus, $ M $ is a right $R$-module.
\end{description}
\end{proof}
\begin{definition}[\textbf{Anti-Ring Homomorphism}]
	Let $R$ and $S$ be two rings with identities $1_r$ and $1_s$ respectively. Define a map $f$
	\[ f : R \rightarrowtail S \] satisfying following properties, for each $a , b \in R$ \newline
	\begin{description}
		\item[(i)] \[ (a+b)f = (a)f +(b)f \]
		\item[(ii)] \[ (ab)f  = (b)f\ (a)f \]
		\item[(iii)] \[ (1_r)f = 1_s \]
  	
	\end{description}
	 Then, $f$	is called anti-ring homomorphism.
\end{definition}
\begin{thm}
	Let\marginnote{\[ M \ \text{is a left R-module} \] \[\centering\Updownarrow \] \[\newline\exists \ f: R \ \xrightarrow[\text{Homo}]{\text{Anti-Ring}} End \ M \] } $R$ be a ring and $M$ be any abelian group with addition. then $M$ is a left $R$-module if and only if there exists a map which is anti-ring homomorphism from $R$ to $End \ M$.
\end{thm}
\begin{proof}
	Left to reader.
\end{proof}
\bigskip
\begin{definition}[\textbf{SubModule}]
	Let $M$ be a left (right) $R$-module then a subset $N$ of $M$ is called a submodule of $M$ if \underline{$N$ is a left (right) $R$-module} \underline{under the operation induced from $M$.}\newline \bigskip
	In other words, A subset $N$ of $M$ is called submodule of $M$ if
	\begin{description}
		\item[(i)] $N$ is subgroup of $M$.
		\item[(ii)] $N$ is closed under induced scaler multiplication from $M$.
	\end{description}
\end{definition}
\bigskip
\begin{thm}[\textbf{Criterion for Checking Modules}]

	Let $M$ be a left (right) $R$-module and $N$ be a subset of $M$ then $N$ is a submodule of $M$ if and only if
	\begin{description}
		\item[(i)]
		\marginnote[2.5em]{\[ \forall \ x , y  \in N \] } \[ x-y \in N \]
		\item[(ii)]
		\marginnote[2.5em]{\[ \forall \ a \in R \ \&\ x \in N \]} \[ a x \in N \]
	\end{description}
\end{thm}
\begin{proof}
	Left to reader.
\end{proof}
\bigskip
\subsection{Examples:}
\begin{enumerate}
	\item As every Vector Space $V$ over a Field $F$ is a $F$-module. So, submodules of $V$ are subspaces of $V$.
	\item As every abelian group $G$ is a $\mathbb{Z}$-module. So, all subgroups of $G$ are submodules.
	\item Let $R$ be a ring then $R$ is a left as well as right $R$-module then left (right) ideals of $R$ are left (right) submodules of $R$.
	\item $\left\{0\right\}$ and $M$ are trivial submodules of any left (right) $R$-module $M$.
\end{enumerate}
\bigskip
\begin{remark}\qquad
	\begin{enumerate}
		\item Union of two submodules need not to be a submodule.\marginnote{Think an example !}
		
		\item Intersection of any number of submodules is again a submodule.\marginnote{\textbf{Hint:} Verify using criterion for checking modules.}
	\end{enumerate}
\end{remark}
\bigskip	

\begin{remark}\textbf{(Smallest Submodule containing a set)}\newline
	  		Let $M$ be any left (right) $R$-module and $S$ be any subset of $M$. Suppose $\mathcal{F}$ be the family of all submodules of $M$ containing $S$. \[  \text{Let} \; P=\bigcap_{N \in \mathcal{F}}N  \] then $P$ is a submodule of $M$ containing $S$ as being intersection of an indexed family of submodules containing $S$.\newline \bigskip Moreover, $P$ is the smallest submodule of $M$ containing $S$. i.e. for any arbitrary submodule $K \in \mathcal{F}$ , we have $ P \subseteq K$. Such submodule $P$ of $M$ is said to be generated by set $S$ and is denoted by \[ P = \left\langle S \right\rangle  = (S) \]
\end{remark}
\bigskip
\begin{remark}\qquad
	\begin{description}
	\item Let $S$ be any subset of left $R$-module $M$ and $\left\langle S \right\rangle $ is the smallest submodule of $M$ containing $S$.\newline
	\begin{enumerate}
		\item if $S$ is non-empty and finite , $S = \left\lbrace x_1,x_2,x_3, \cdots , x_n \right\rbrace $ \[ \left\langle S \right\rangle = \left\langle \left\lbrace x_1,x_2,x_3, \cdots , x_n \right\rbrace \right\rangle  = \left\langle x_1,x_2,x_3, \cdots , x_n \right\rangle \] is said to be a finitely generated by $S$ and is smallest submodule of $M$ containing $S$.
		\item if $S = \phi$ \quad i.e. $S$ is an empty set \[ \left\langle S \right\rangle = \left\langle \phi \right\rangle = \left\lbrace 0 \right\rbrace \]
		\item if $S = \left\lbrace a\right\rbrace $ \quad i.e. $S $ is singleton then $\left\langle S \right\rangle = \left\langle a\right\rangle $ is said to be a \underline{cyclic submodule}.
	\end{enumerate}
\end{description}
\end{remark}
\bigskip
\begin{definition}[\textbf{Cyclic module}]   \cite{Cohn2005}
	A module $M$ is said to be a cyclic module if it can be   generated by a single element.
\end{definition}
\textit{For Example:}
	A ring $R$ over itself is a module and can be generated by identity element $ \left\lbrace 1\right\rbrace $ so is a cyclic module.
\bigskip
\begin{thm}
	Let $M$ be left $R$ module and $S$ being any subset of $M$.
	\begin{equation*} \left\langle S\right\rangle = \begin{cases}
	\left\lbrace 0\right\rbrace & \text{if $S = \phi$} \\ \left\lbrace \sum\limits_{i \in J_n} a_i x_i \ \middle\vert \  a_i \in R \ , x_i \in S\right\rbrace  & \text{otherwise}
	\end{cases}
	\end{equation*}
\end{thm}
\begin{proof}
\begin{description}
	\item[Case-I] Let us suppose that $S = \phi $ ,as $ \left\langle S\right\rangle $ is the intersection of all the submodules of $ M $ containing $S$\marginnote[-2em]{i.e. Every submodule of $M$ will contain $S$}. \newline \bigskip In particular, $ \left\lbrace 0\right\rbrace  $ also contains $S$ i.e. \[ \left\lbrace 0\right\rbrace  \in\mathnote{$\because \ \mathcal{F} \ \text{is a collection of all submodules of}\ M \newline \text{containing}\ S$ } \mathcal{F}  \]
	so, \begin{align*} \left\langle S\right\rangle &= \bigcap_{N \in \mathcal{F}}N  \\& = \left\lbrace 0\right\rbrace   \end{align*}
    \item[Case-II] Suppose $S$ is non-empty and let    \[ P = \left\lbrace \sum\limits_{i \in J_n} a_i x_i \ \middle\vert \  a_i \in R \ , x_i \in S\right\rbrace\]
         First , we'll show that $S\subseteq P$ \newline
         Let $x \in\ S$ then it can be expressed in following form:
         \[x = 1.x = \sum\limits_{i \in J_1} a_i x_i \] \marginnote[-2.5em]{with $a_1 = 1$ and $x_1 = x $}
         \[\therefore x \in  P \Rightarrow S \subseteq P \]  \marginnote[-2em]{$\because x$ was chosen arbitirary.}
         Now ,we'll show that $P$ is a submodule of $M$ using submodule criterion.           \newline
         Let $u\ ,\ v \in P$ . so, we need to show $u + \alpha v \in P$ \marginnote{for any $\alpha\in R$}
         \[u = \sum\limits_{i\in J_n} a_i x_i\] \marginnote[-2em]{$\forall x_i \in S \ \&\ a_i \in R$}
          \[v = \sum\limits_{j\in J_m} b_j y_j\]  \marginnote[-2em]{$\forall y_j \in S \ \&\ b_j \in R$}
          define, for any $\alpha \in R$
          \begin{align*} z_k = x_k \qquad ,\qquad c_k = a_k     \mathnote{$k \in J_n$}  \\
           z_{k+j} = y_j \qquad , \qquad c_{k+j} = \alpha b_j    \mathnote{$j \in J_m$}  \end{align*}
          Thus, we have
           \begin{align*}
            u+ \alpha v &= \sum\limits_{i\in J_n}a_i x_i + \alpha \sum\limits_{j\in J_m}b_j y_j  \\
             & =\sum\limits_{i\in J_n}a_i x_i + \sum\limits_{j\in J_m}\alpha b_j y_j  \\
             &= \sum\limits_{k\in J_n}c_k z_k + \sum\limits_{k = n+1}^{n+m} c_k z_k  \\
             &=  \sum\limits_{k \in J_{n+m}} c_k z_k
          \end{align*}
          so, $P$ is a submmodule of $M$ containing $S$.
          \newline Now, we'll show that $P$ is \underline{smallest} submmodule of $M$ containing $S$.
          \newline \bigskip
          Let $K$ be any arbitirary submodule of $M$ containing $S$
           \[\text{i.e.} \ K \ \in \mathcal{F}\]
          $\because  \ \ \ K $ is a submodule and $S \subseteq K$ \newline
          $\therefore \  K$  is closed under scaler multiplication and addition.
          \[\text{i.e}\qquad \sum\limits_{i \in J_n} a_i x_i  \in K \]  \marginnote[-2.5em]{$\forall \ a_i \in R \ \& \ x_i \in S $}
          so , \[P =\left\langle S\right\rangle \subseteq K \]
               Hence,  $P$ is smallest submmodule of $M$ containing $S$.
           \end{description}	
	
	
\end{proof}
\bigskip
\begin{defn}[\textbf{Generating Set / Set of Generators}]
A set of generators for a left (right) $R$-module $M$ is a subet $S$ of $M$ such that
\[M = \left\langle S\right\rangle \]
if no proper submodule of $M$ contains $S$ then $S$ generates $M$ (verify ?)
\end{defn}
\bigskip
\subsection{Examples}
\begin{description}
  \item[1.] A   ring $R$ considered as left (right) $R$-module is generated by identity element $\lbrace1\rbrace$

  \item[2.] $\mathbb{Z}\times \mathbb{Z}$  over $ \mathbb{Z}  $ can be generated by
  \[S =\left\lbrace(0,1),(1,0)\right\rbrace\]
  \item[3.] All finite dimensional vector space can be generated by it's basis (finite), so is finitely generated submodule.
  \item[4.] Let $R$ be a ring, $I$ be left(right) ideal of $R$ then it is a left(right) $R$-module. So, every  finitely  generated left(right) ideals of $R$ are finitely generated submodule.
  \item[5.] A submodule of left $R$-module is cyclic iff it is prinicipal ideal of $_RR$.
\end{description}
\bigskip
\begin{defn}
  Let $M$ be a left $R$-module and $\left\lbrace N_\alpha\right\rbrace_{\alpha \in \Omega }$ \marginnote{where $\Omega$ is indexing set. } be family of submodules of $M$ then sum $\sum\limits_{\alpha \in \Omega } N_\alpha $ is defined to be a submodule of $M$ generated by $\bigcup\limits_{\alpha \in \Omega}N_\alpha $  \[\left\langle \bigcup_{\alpha \in \Omega}N_\alpha \right\rangle = \sum\limits_{\alpha \in \Omega } N_\alpha \] \bigskip
   Moreover, $\sum\limits_{\alpha \in \Omega } N_\alpha $ is smallest submodule of $M$ containing $N_\alpha $ \marginnote[-2em]{for each $\alpha \in \Omega$}
  \end{defn} \bigskip
  \begin{prop}
    Let $M$ be a left $R$-module and $\left\lbrace N_\alpha\right\rbrace_{\alpha \in \Omega }$ \marginnote{where $\Omega$ is indexing set. } be family of submodules of $M$ then sum \[\sum\limits_{\alpha \in \Omega } N_\alpha =\left\lbrace \sum\limits_{\alpha \in \Omega } x_\alpha \middle\vert\, x_\alpha \in N_\alpha \quad ,\  x_\alpha = 0 \; \textmd{for almost all} \; \alpha  \right\rbrace \] \marginnote[-2em]{for each $\alpha \in \Omega$}
    \begin{proof}
      Let \[P = \left\lbrace \sum\limits_{\alpha \in \Omega } x_\alpha \middle\vert\, x_\alpha \in N_\alpha \quad , \ x_\alpha = 0 \; \textmd{for almost all} \; \alpha\right\rbrace \]
      We need to show that $P$ is smallest submodule of $M$ containing each $N_\alpha$
      \newline  \bigskip
      \textbf{Claim 1 :}.  \qquad $P$ is submodule of $M$  \newline Clearly, $P$ is non-emptpy. Taking $x_\alpha = 0$ for each $\alpha \in \Omega$, we have \[\Rightarrow0 \in P\] Also, for a fixed but arbitirary $\alpha \in \Omega $ taking \[ x_i = \begin{cases}
                                 x, & \mbox{if } i =\alpha \\
                                 0, & \mbox{otherwise}.
                               \end{cases}\]
            so $x =\sum x_\alpha \in P$ 
       \end{proof}
  
    
     \end{prop} 